<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{Processing several measurement cycles}
-->

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(out.extra='style="display:block; margin: auto"'
    #, fig.align="center"
    , fig.width=4.3, fig.height=3.2, dev.args=list(pointsize=10)
    , message=FALSE
    , results='hold'
    )
knit_hooks$set(spar = function(before, options, envir) {
    if (before){
        par( las=1 )                   #also y axis labels horizontal
        par(mar=c(2.0,3.3,0,0)+0.3 )  #margins
        par(tck=0.02 )                          #axe-tick length inside plots             
        par(mgp=c(1.1,0.2,0) )  #positioning of axis title, axis labels, axis
     }
})
# genVigs("severalCycles")
```

Processing several measurement cycles
==============================================

```{r eval=FALSE, echo=FALSE, results='hide'}
isDevelopMode <- TRUE
library(twDev)
setwd('..');loadPkg()
```
```{r results='hide', warning=FALSE}
if(!exists("isDevelopMode")) library(RespChamberProc)
set.seed(0815)      # for reproducible results
```

Determine subsets of single measurment cycles
---------------------------------------------------

First, the data is loaded. Here, directly from zipped logger-output.
```{r, spar=TRUE, fig.width=12}
fName <- system.file("genData/SMANIE_Chamber1_26032015.zip", package = "RespChamberProc")
if( nzchar(fName) ){ ds <- ds0 <- readDat(unz(fName, file=unzip(fName, list=TRUE)[1,"Name"] ),tz="UTC") }
head(ds)
plot( CO2_LI840 ~ TIMESTAMP, ds, ylab="CO2 (ppm)", xlab="Time")
```

The dataset contains several measurment cycles of light and dark chambers with increasing or decreasing concentations respectively.

First, we correct the pressure to standard units and correct the CO2
concentrations for water vapour.
```{r}
ds$Pa <- ds0$AirPres * 100  # convert hPa to Pa
ds$CO2_dry <- corrConcDilution(ds, colConc = "CO2_LI840", colVapour = "H2O_LI840")
ds$H2O_dry <- corrConcDilution(ds, colConc = "H2O_LI840", colVapour = "H2O_LI840")
ds$VPD <- calcVPD( ds$SurTemp, ds$Pa, ds$H2O_LI840)
```

In order to process each measurement cycle independently, we first determine parts of the time series that are contiguous, i.e. without gaps and without change of an index variable, here variable `collar`.


```{r}
dsChunk <- subsetContiguous(ds, colTime="TIMESTAMP", colIndex="Collar") 
head(dsChunk)
```

The new modified contains a new variable, `iChunk`, holding a factor that
changes with different measurment cycles.
This factor can be used to select subset of single measurement cycles. 
```{r , spar=TRUE}
dss <- subset(dsChunk, iChunk==15)
plot( CO2_dry ~ TIMESTAMP, dss, ylab="CO2 (ppm)", xlab="time (Minute:Second)")
```

Computing the flux
------------------

Function `calcClosedChamberFluxForChunks` helps you with subsetting the data and applying function `calcClosedChamberFlux` to each subset.

```{r}
# for demonstration use only the first 20 cycles
dsChunk20 <- subset(dsChunk, as.integer(iChunk) <= 20) 
chamberVol=0.6*0.6*0.6		# chamber was a cube of 0.6m length
surfaceArea=0.6*0.6

resChunks1 <- calcClosedChamberFluxForChunks(dsChunk20, colTemp="T_LI840"
    ,fRegress = c(lin = regressFluxLinear, tanh = regressFluxTanh)	# linear and saturating shape
    ,debugInfo=list(omitEstimateLeverage=TRUE)	# faster
    ,volume=chamberVol
    ,area=surfaceArea
)
head(resChunks1)
```

The results are similar as for `calcClosedChamberFlux`, unless there are several rows identified by additional key column iChunk.

## Plotting faceted data and fits
```{r eval=FALSE, echo=FALSE}
library(twDev)
reloadPkg("RespChamberProc")
```
Plot the results to dectect problems. 
```{r, spar=TRUE, fig.width=11, fig.height=6, warning=FALSE, message=FALSE}
library(ggplot2)
plots <- plotCampaignConcSeries( dsChunk20, resChunks1, plotsPerPage=64L)  
print(plots$plot[[1]]) # print the first page
```

If argument `fileName` is provided to `plotCampaignConcSeries`. All plots are
written to a pdf. If there are more cycles, i.e. plots, than argument `plotsPerPage`(default 64) there will be several pages in the pdf.




