<!--
%\VignetteEngine{knitr}
%\VignetteIndexEntry{CO2 fluxes from Chamber CO2 concentrations}
-->

```{r setup, include=FALSE}
library(knitr)
opts_chunk$set(out.extra='style="display:block; margin: auto"'
    #, fig.align="center"
    , fig.width=4.3, fig.height=3.2, dev.args=list(pointsize=10)
    , message=FALSE
    , results='hold'
    )
knit_hooks$set(spar = function(before, options, envir) {
    if (before){
        par( las=1 )                   #also y axis labels horizontal
        par(mar=c(2.0,3.3,0,0)+0.3 )  #margins
        par(tck=0.02 )                          #axe-tick length inside plots             
        par(mgp=c(1.1,0.2,0) )  #positioning of axis title, axis labels, axis
     }
})
# genVigs("singleSeries")
```

CO2 fluxes from Chamber CO2 concentrations
======================================================

```{r eval=FALSE, echo=FALSE, results='hide'}
isDevelopMode <- TRUE
library(twDev)
setwd('..');loadPkg()
```

```{r results='hide', warning=FALSE}
if(!exists("isDevelopMode")) library(RespChamberProc)
set.seed(0815)      # for reproducible results
```

Preparing the chamber data
------------------------------

First, the data is loaded. This is a typical data.frame as obtained from a
logger file of a light chamber with photosynthetic plants in it, for a single
chamber measurement cycle. For timestamps spaced about every second, the
sensor readings from CO2 concentration in ppm, vater vapour in ppm, chamber
temperaturein degree Celsius and air pressure, here in kPa are recorded.

```{r, spar=TRUE}
data(chamberLoggerEx1s, package="RespChamberProc")
ds <- chamberLoggerEx1s
head(ds)
plot( CO2_Avg ~ TIMESTAMP, ds, ylab="CO2 (ppm)", xlab="time (Minute:Second)")
```

RespChamberProc demands the pressure in units Pascal, so we need to convert from
kPa. 
```{r}
ds$Pa <- chamberLoggerEx1s$Pa * 1000  # convert kPa to Pa
```

RespChamberProc works with concentrations of CO2 per dry air. There was
vater vapour in the chamber and CO2 concentrations are measured per wet air. We
need to compute the concentrations per dry air.
```{r}
conc <- ds$CO2_dry <- corrConcDilution(ds)
```

Computing the flux
---------------------
The CO2-flux is the change of concentration per time, i.e. the slope of the
concentration change. Usually, the changing concentration within the chamber
over time decreases the slope voer time. Hence, RespChamberProc fits several
functional forms to the CO2~time relationship and reports the intial slope of
the best-fitting form.

```{r}
resFit <- calcClosedChamberFlux(ds
		, colConc = "CO2_dry", colTime = "TIMESTAMP"	# colum names conc ~ timeInSeconds
		, colTemp = "TA_Avg", colPressure = "Pa"		# Temperature in K, Pressure in Pa
		, volume = 1, area = 1						    # chamber dimensions m3 and m2
)
```

`calcClosedChamberFlux` expects the time in seconds. Providing a vector
of POSIXct is ok.
Moreover, the dimensions of the chamber must be given, the inside chamber air
volume in cubic meter, and the area (in square meter) of the exchange area
between the chamber and the studied object. This area is usually the area of the
open bottom side ofthe chamber. 

If the chamber encloses an objects, set the area to 1 and interpret the flux in
micromol/second instead of micromol/square meter/second.

In order to convert (change of) concentrations to amount of substance, the pressure (in Pa) and temperature (in Kelvin) inside
the chamber are required in addition to volume in order to apply the idal gas law.  
The flux is proportional to pressure. Hence, if pressure is not recorded with
the logger file, one may compute with a average pressure of Pa=100*1000, and
correct fluxes post-hoc when an esitmate of air pressure becomes available
from meteorological data.


Inspecting the results
-------------------------

Its a one-row tibble, i.e. a kind of tabular data like a data.frame, with fitting statistics and fitted model objects. While all the first columns are numeric, column `times` holds a vector of times after lag-phase for which concentration predictions have benn made by the model object given in column `model` (see explanations on the graph below).

```{r}
resFit
```

The most important information are the estimate of the flux, and its
uncertainty, both in unit mumol/m2/s:
```{r}
resFit[,c("flux","sdFlux")]
```

Or in gC/m2/day:
```{r}
fluxInMuMol <- unlist(resFit[,c("flux","sdFlux")])
convert_mumolPers_to_gPerday(fluxInMuMol)
```


The results can be visualized in a plot:
```{r , spar=TRUE}
plotResp(ds, resFit, label="Example Series")		
```

The fitted form (solid line) approximates the change of measured concentration
(points) over time. Usually there is a lag-time (dotted vertical line) between
concentration change, and when the time when the signal reaches the sensor. The
flux after the intial lag-time is reported at the top left together with its
uncertainty in mumol/m2/s.
The label can be provided to distinguish different measurement cycles.
